---
title: "Title of your paper goes here"
# If blank, the running header is the title in upper case.
shorttitle: "PSYCH 2127 - Scientific Method / Analysis II"
# Set names and affiliations.
# It is nice to specify everyone's orcid, if possible.
# There can be only one corresponding author, but declaring one is optional.
author:
  - name: Your Name Here
    # Roles are optional. 
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    affiliations:
      - id: id1
        name: "Laurentian University"
        group: Undergrad Psychology Program
        department: Dr. Emond
abstract: "One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words **here we show** or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline."
# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
keywords: [cognitive bias, representativeness heuristic, keyword3]
# If true, tables and figures are mingled with the text instead of listed at the end of the document.
floatsintext: false
# Numbered lines (.pdf and .docx only)
numbered-lines: false
# File with references
bibliography: bibliography.bib
# Suppress title page
suppress-title-page: false
# Masks references that appear in the masked-citations list
mask: false
lang: en
language:
  citation-last-author-separator: "and"
  title-block-author-note: "Author Note"
format:
  apaquarto-pdf: default
---

```{r}
#| label: setup
#| include: false

# HERE IS WHERE YOU WILL ADD ANY EXTRA PACKAGES YOU NEED.
# Copy and paste any packages from the original Markdown file you played with into here.
# Remember, a package can't be loaded if it is not installed.

library(tidyverse)
library(DataExplorer)
library(sjPlot)
library(ggplot2)
library(ggstatsplot)
library(modelsummary)
#library(aov)
library(lme4)
library(ggpubr)
library(rstatix)

# To install packages run the following code in the console pane:

# install.packages("packagenamehere")
library(conflicted)
library(flextable)
library(ftExtra)
library(officer)
library(knitr)

conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)
```

This is my introductory paragraph. The title will be placed above it automatically. *Do not start with an introductory heading* (e.g., "Introduction"). The title acts as your Level 1 heading for the introduction.

Here you will add your **brief** literature review which should include a bit of background citing the papers you read in your initial research. You will also state your purpose, your hypotheses and justifications for them.

You can copy and paste your write up for these sections from Word or Google Docs directly into R Markdown. You can also write directly in R Markdown like I do, but I recommend the former in the beginning. Baby steps!

## Hypotheses, Aims, and Objectives

The last paragraph of the introduction usually states the specific hypotheses of the study, often in a way that links them to the research design.

# Method

General remarks on method. Here you will report your study design, including sample size, independent and dependent variable(s) and any other important bits.

## Participants

Who are they? How were they recruited? Report criteria for participant inclusion and exclusion. Perhaps some basic demographic stats are in order. A table is a great way to avoid repetition in statistical reporting.

## Measures

This section can also be titled **Materials** or **Apparatus**. Whatever tools, equipment, or measurement devices used in the study should be described.

### Measure A

Describe Measure A.

### Measure B

Describe Measure B.

## Procedure

What did participants do?

How are the data going to be analyzed?

# Results

## Descriptive Statistics

Here we describe the basic characteristics of our primary variables (see @tbl-table01 and @tbl-table02)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#| label: tbl-table01 # this labels the table Table 2
#| tbl-cap: "Descriptive Statistics Option 2"
#| ft.align: left
#| apa-note: A note below the table
# Here you will conduct your analyses. I will give you detailed instructions on what analyses/packages to use for your specific analyses. I will send this with your data.

# Here are a couple of example that you can delete once you have your own analyses.

# https://www.datanovia.com/en/lessons/anova-in-r/ <- in depth tutorial

# let's load the iris data for now but for your study you'll add the data I sent you. Place that data in the same folder as this document (the APA folder of your project) then type df <- read.csv("mydata.csv")

df <- data.frame(PlantGrowth) # we'll pretend this plantgrowth data is your data for now

# here's a little descriptive table of your groups and means within each group

df %>% group_by(group) %>% 
  summarise(n=n(), mean=mean(weight)) %>%  
  flextable()


# Another summary table
```

```{r}
#| label: tbl-table02 # this labels the table Table 2
#| tbl-cap: Descriptive Statistics
#| ft.align: left
#| apa-note: A note below the table


df %>%
  group_by(group) %>%
  get_summary_stats(weight, type = "mean_sd") %>% flextable() %>% theme_apa()

```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4}
#| label: fig-histogram01 # this labels the table Table 2
#| fig-cap: "Histogram of Outcome"
#| ft.align: left
#| apa-note: A note below the figure

hist(df$weight, xlab="Weight", ylab="Frequency", main=" ") # here is a histogram of your outcome

```

```{r}
#| include: FALSE
#| echo: FALSE

library(report)

contrasts(df$group) <- contr.sum(3) # set sum contrasts to mimic aov

# Compute the analysis of variance
res.aov <- aov(weight ~ group, data = df)
# Summary of the analysis
summary(res.aov)

report(res.aov)
TukeyHSD(res.aov)

library(multcomp)
summary(glht(res.aov, linfct = mcp(group = "Tukey")))

```

```{r, fig.height=4}
#| echo: FALSE
#| label: fig-outcome02
#| fig-cap: "The effect of treatment 1 and 2 on weight compared to control"
#| ft.align: left
#| apa-note: A note

contrasts(df$group) <- contr.sum(3)

df %>% 
  ggplot(aes(x=group, y=weight, colour=group))+
  geom_point()+ 
  geom_boxplot(stat="boxplot")

```

The main effect of the treatment was statistically significant and large (F(2, 27) = 4.85, p = 0.016; Eta2 = 0.26, 95% CI \[0.04, 1.00\]). However, post hoc comparisons reveal that while plant growth was higher in treatment 2 compared to treatment 1 (p \<.016), the effect was not significantly better than no treatment at all (p=.3909) (See @fig-outcome02)

<!-- Add Additional Sections as Needed -->

# Discussion

Describe results in non-statistical terms. <!-- Add sections as needed. -->

## Limitations and Future Directions

Every study has limitations. Based on this study, some additional steps might include...

## Conclusion

Let's sum this up.

# References

## Citations

See [here](https://quarto.org/docs/authoring/footnotes-and-citations.html) for instructions on setting up citations and references.

A parenthetical citation requires square brackets [@CameronTrivedi2013]. This reference was in my bibliography file. An in-text citation is done like so: @CameronTrivedi2013.

See [here](https://wjschne.github.io/apaquarto/writing.html#references) for explanations, examples, and citation features exclusive to apaquarto like masked citations (citations masked for peer review) and possessive citations (e.g., "@schneider2012cattell ['s] idea seemed reasonable at the time.")

<!-- References will auto-populate in the refs div below -->

::: {#refs}
:::

<!-- Delete Appendix if not needed. -->
